HEP Software Foundation Community White Paper Working Group -- Training, Staffing and Careers

### 2018-06-22 CWP/papers/HSF-CWP-2017-02_training/latex/cwp-wg-training-careers.tex
rewrite

In the context of web-based training, if the HSF helps to constitute a living
collection of online tutorials, we could organize regular events such as
a ``Tutorial of the month'', or some sort of ``like'' system. The
best authors must be recognized, so that they can showcase their most popular
online tutorials, just the same as their publications.

>>>>

In the context of web-based training, if the HSF helps to constitute a living
collection of online tutorials, we could organize regular events such as
a ``Tutorial of the month'', or some sort of ``like'' system for the students
to support their favorite tutorials. The best authors must be recognized, so
that they can showcase their most popular online tutorials, just the same as
their research publications.
